---
title: "Full run"
author: "Kamil Bakowski"
output: 
  html_document: 
    keep_md: yes
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}
library(svglite)
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
  dev = "svglite",
  fig.ext = ".svg"
)
```
## Script for analysis of multiple FCS plates with data-driven preprocessing and gating
##### **It requires a csv file with a list of directories containing FCS files**
##### **It also use wellAnnotation table saved to csv in the same directory**
##### *wellAnnotation specify Well.ID, Strain, Screening No, and control samples*

```{r load}
library(flowCore)
library(flowViz)
library(flowDensity)
library(flowStats)
library(plateCore)
library(flowClust)
```
## pre-define more complicated functions used lated with `fsApply`
```{r functions for clean, gate and SD with fsapply}
#rm functions each time when optimizing
# rm(multiClean)
# rm(multiGate)

rectangClean <- function(x){
  higherbound <- deGate(x, channel = "SSC.A", use.percentile = TRUE, percentile = 0.90)
  cellsH <- flowDensity(x, channels = c("FSC.A", "SSC.A"), position = c(NA, F), gates = c(NA,higherbound))
  rectSub <- notSubFrame(cellsH, c("FSC.A","SSC.A"), position = c(F,NA), gates = c(25000,NA))
  rectSubFS <- getflowFrame(rectSub)
}

multiGate <- function(x){
  
  
  xgated <- flowDensity(x, channels = c("FSC.A", "B535.345.A"), position = c(NA, T),ellip.gate=FALSE, gates = c(NA,ctrgate))
  #part for automatic ploting and saving as png. It iterates filenames and plotnames with Plot ID defined in `for` loop and Well ID directly from fsapply FUN
  #setup save directory to existing folder with specified iterative name and extension. Specify name with paste function. 
  GUID <- identifier(x)
  plottitle = paste(pName,"Gated",GUID)
  savepath=file.path("C:/Users/KozakPC/Documents","R/Cyto","Plots",plottitle)

  #define file extension, plot with gate and close
  png(filename = paste(savepath,".png"))
  plotDens(getflowFrame(xgated), channels = c("B535.345.A", "FSC.A"), xlim = c(0, 25000), ylim= c(0,250000),xlab = "mVenus",ylab = "FSC-A", main = plottitle)
  #lines(ctrgate@filter, type = "l")
  dev.off()
  
  positives <- getflowFrame(xgated)
}
#Calculating Median Absolut Deviation and Standard Deviation requires transformation of flowFrame to matrix
extractMAD <- function(x){
  matrixCG <- exprs(x)
  MAD <- mad(matrixCG[,"B535.345.A"])
}
extractSD <- function(x){
  matrixCG <- exprs(x)
  SD <- sd(matrixCG[,"B535.345.A"])
 }
```
```{r}
#rm(Totres.list)
#rm(Total.results)
#rm(Cclean.list)
```

## setup for mulitplate analysis
```{r for loop with nested fsApply, message=FALSE}
longLoP <- read.csv("C:/Users/KozakPC/Documents/R/Cyto/Corrected.csv", stringsAsFactors = FALSE)
Totres.list <- list()
Total.results <- data.frame()
Cclean.list <- list()
for (i in 1:nrow(longLoP)){
  path <- longLoP[i,]
  setwd(path)
  ##Load path and files to flowSet
  wellAnnotation <- read.csv("wellAnnotation.csv", header = TRUE, stringsAsFactors = FALSE)
  pFS <- read.flowSet(path = path,pattern = ".fcs",name.keyword = "WELL ID",alter.names=TRUE)
  
  #use pName for iterative name in all saved pngs
  pName <- paste("Plate",i)
  
  cleanedFS <- fsApply(pFS, rectangClean)
  
  
  ##Pass cleaned flowSet for gating
  ###test for existance of data and pick first encountered. There is always at least one well between A and D.
  ctrwell <- ifelse(any(rownames(pData(pFS)) == "A12"),"A12",
                  (ifelse(any(rownames(pData(pFS)) == "B12"),"B12",
                          (ifelse(any(rownames(pData(pFS)) == "C12"),"C12","D12")))))
  ctrWELL12 <- cleanedFS[[ctrwell]]
  ctrgate <- deGate(ctrWELL12, channel = "B535.345.A", use.percentile = TRUE, percentile = 0.85)
  
  gatedFS <- fsApply(cleanedFS, multiGate)
  
  ##pass to plate set
  pGatedFS <- flowPlate(gatedFS, wellAnnotation, plateName = pName)
  
  ##extract stats, combine to data.frame and save to a separate list
  #Possible to calculate MFIs and MFI ration to controls, but gives error with negative or very low count, I guess [0:1]
  #plateFSstats <- summaryStats(pGatedFS)
  df.results <- pGatedFS@wellAnnotation
  
  #cell No
  cellsClean <- fsApply(cleanedFS, nrow)
  colnames(cellsClean) <- c("Total_CellNo")
  df.cellsClean <- data.frame(cellsClean)
  
  #Used for QC
  cleanNo.name <- paste("Total Cell No.", pName)
  savepath.cleanNo = file.path("C:/Users/KozakPC/Documents","R/Cyto","Results",cleanNo.name)
  svg(filename = paste(savepath.cleanNo, ".svg"), width = 6, height = 5)
  par(mar=c(5,5,4,1)+0.1)
  barplot(margin.table(cellsClean,1), ylim= c(0,10000), main= cleanNo.name, cex.main=1.5, xlab = "Wells", cex.lab=1.2, cex.names=0.25, las=2, col = "darkgreen")
  title(ylab = "No. of cells", line = 3.4, cex.lab=1.2)
  dev.off()
  
  cellsGated <- fsApply(gatedFS, nrow)
  colnames(cellsGated) <- c("Positives_CellNo")
  df.cellsGated <- data.frame(cellsGated)
  
  gatedNo.name <- paste("Gated Cell No.", pName)
  savepath.gatedNo = file.path("C:/Users/KozakPC/Documents","R/Cyto","Results",gatedNo.name)
  svg(filename = paste(savepath.gatedNo, ".svg"), width = 6, height = 5)
  par(mar=c(5,5,4,1)+0.1)
  barplot(margin.table(cellsGated,1), ylim= c(0,10000), main= gatedNo.name, cex.main=1.5, xlab = "Wells", las=2, cex.lab=1.2, cex.names=0.25, col = "darkgoldenrod2")
  title(ylab = "No. of cells", line = 3.4, cex.lab=1.2)
  abline(h=cellsGated[identifier(ctrWELL12),], col = "black", lty = 1, lwd = 1)
  dev.off()
  
  #MAD
  MAData <- fsApply(gatedFS, extractMAD)
  colnames(MAData) <- "MAD"
  df.MAD <- data.frame(MAData)
  df.MAD
  
  #SD
  SData <- fsApply(gatedFS, extractSD)
  colnames(SData) <- "SD"
  df.SD <- data.frame(SData)
  
  #summary
  sumwells <- fsApply(gatedFS, function(x){sum_s <- summary(x)[,8]})
  df.sw <- data.frame(sumwells)
  
  df.resultsm <- merge(x=df.results, y=df.cellsClean, by.x="Well.Id", by.y = 0, all.x=TRUE)
  df.resultsn <- merge(x=df.resultsm, y=df.cellsGated, by.x="Well.Id", by.y = 0, all.x=TRUE)
  df.resultso <- merge(x=df.resultsn, y=df.sw, by.x="Well.Id", by.y = 0, all.x=TRUE)
  df.resultsp <- merge(x=df.resultso, y=df.MAD, by.x="Well.Id", by.y = 0, all.x=TRUE)
  mdf.results <- merge(x=df.resultsp, y=df.SD, by.x="Well.Id", by.y = 0, all.x=TRUE)
  mdf.results$i <- i
  Totres.list[[i]] <- mdf.results
}
#make a full data.frame from list of results
Total.results = do.call(rbind,Totres.list)
head(Total.results)
tail(Total.results)
#remove "name" column as its redundant and class=list which prevents export to csv
Total.results$name <- NULL
write.csv(Total.results, file = "C:/Users/KozakPC/Documents/R/Cyto/Results/ResultsTable_correct.csv")
```

